%\VignetteIndexEntry{FLBEIA manual}
%\VignetteEngine{R.rsp::tex}
%\VignetteKeyword{FLBEIA}
%\VignetteKeyword{manual}

\documentclass{article}
% ----------------------------------------------------------------
\usepackage{natbib,amsmath,amsthm,amsfonts,amssymb,fancyhdr}
\usepackage{Sweave} %
\usepackage{graphicx}
\usepackage[section]{placeins}
\usepackage[flushleft]{threeparttable}
\usepackage{pdflscape}


\setcounter{tocdepth}{4}

\newcommand{\pd}[2]{\frac{\partial #1}{\partial #2}}
\newcommand{\lap}[2]{\frac{\partial^2 #1}{\partial #2^2}}
\newcommand{\mean}{\text{mean}}

%% Change margins
\addtolength{\oddsidemargin}{-.875in}
\addtolength{\evensidemargin}{-.875in}
\addtolength{\textwidth}{1.75in}
\addtolength{\topmargin}{-.875in}
\addtolength{\textheight}{1.75in}
%%

\begin{document}
\input{FLBEIA_manual-concordance}

\title{Technical manual for \texttt{FLBEIA} a \texttt{R} package to conduct Bio-Economic Impact assessments using \texttt{FLR} (version 1.15)}

\author{Dorleta Garc\'ia, Ra\'ul Prellezo, Sonia S\'anchez, Marga Andr\'es, Agurtzane Urtizberea \\ \& Itsaso Carmona}

%\date{}
\date{\today}

\maketitle

\abstract{\texttt{FLBEIA} (FL Bio-Economic Impact Assessment) is an \texttt{R} package build on top of \texttt{FLR} libraries. The purpose of the package is to provide a flexible and generic simulation model, also called FLBEIA, to conduct Bio-Economic Impact Assessments of harvest control rule based on management strategies under a Management Strategy Evaluation (MSE) framework. The model is divided into two main blocks, the operating model (OM) and the management procedure model (MPM). The OM is formed by the biological, the fleet and the covariates components and the MPM by the observation, the assessment and the management advice components.The model is multistock, multifleet and seasonal, and uncertainty is introduced by means of montecarlo simulation. The algorithm has been coded in a modular way to ease its checking and to make it flexible. 
The package provides functions that describe the dynamics of the different model components and the user chooses which of the functions are used in each specific case study. Furthermore, for some of the components, if the functions provided within \texttt{FLBEIA} do not fulfill the requirements of a specific case study, the user can code the functions that describe better the dynamics of those components. Therefore, due to the wide choice of functionality and flexibility that provides the model, we can define it as a framework more than as a model. Main limitations of the model are that 
the stocks must be age structured or aggregated in biomass (length structure is not allowed), and that spatial dimension is not considered explicitly. However, spatial characteristics could be modeled assigning stocks and/or fleets/metiers to specific areas.
}


\newpage

\tableofcontents
\clearpage{\pagestyle{empty}\cleardoublepage}


\input{01_Introduction}

\input{02_Concept_Of_FLBEIA}

\input{03_Running_FLBEIA}

\input{04_FLBEIA_FIRST_level_Func}

\input{05_FLBEIA_SECOND_level_Funcs}

\input{06_FLBEIA_THIRD_level_Funcs}

\input{07_FLBEIA_FOURTH_level_Funcs}

\input{08_FLBEIA_Smart_Conditioning}

\input{09_FLBEIA_Output_Summary}

\input{10_Acknowledgements}

\bibliographystyle{plainnat}
\bibliography{00_MSE_Algorithm_Bibliography}

%\input{08_Utilities}
\newpage

\appendix

\input{A1_New_Classes}
\input{A2_FLR_objects_Graphics}
\input{A3_Control_objects_tables}
\input{A4_SmartConditioning_tables}

%\include{A1_Notation}


\end{document}
