
\section{Running \texttt{FLBEIA}} \label{sec:FLBEIArun}

\subsection{Input objects}

  \texttt{FLBEIA} requires some input arguments to run a simulation. There are two types of arguments: the main arguments, which give information on 
  the stocks, the fleets and the covariates, and the control arguments, which control the behaviour of the main and the second level functions 
  (see Section~\ref{sec:2ndlvl}). The main arguments contain biological information on the stocks (\texttt{biols}, \texttt{SRs} and 
  \texttt{BDs}), information on the fleets (\texttt{fleets}), additional variables (\texttt{covars}) and information on management 
  (\texttt{indices}, \texttt{advice}). Regarding the control arguments, there is a control object related to the main function 
  \texttt{FLBEIA} (\texttt{main.ctrl}), whereas the others relate to the main arguments (\texttt{biols.ctrl}, \texttt{fleets.ctrl}, 
  \texttt{covars.ctrl}, \texttt{obs.ctrl}, \texttt{assess.ctrl}, \texttt{advice.ctrl}).
  For detailed information on the input objects required see Section~\ref{sec:1stlvl}.
  
  In order to easy the creation of the objects with the appropriate object format some additional functions has been implemented to create the inputs 
  (see Section~\ref{sec:SmartCondFun}). Additionally, several examples has been coded for guidance (see Section~\ref{sec:SmartCondEx}).
  
\subsection{Main function: \texttt{FLBEIA}}

  To perform biological and economic simulations it is necessary to invoke the main function, \texttt{FLBEIA}, which calls to different subfunctions 
  to perform the simulations depending on the control elements set.
  
  \noindent \texttt{FLBEIA} function is called as follows:
  
  \begin{center}
    \texttt{FLBEIA(biols, SRs, BDs, fleets, covars, indices, advice, 
            main.ctrl, biols.ctrl, fleets.ctrl, covars.ctrl, obs.ctrl, assess.ctrl, advice.ctrl) }
	\end{center}
  
  For more details on the \texttt{FLBEIA} function see Section~\ref{sec:1stlvl}.

\subsection{Output object}

  The output of \texttt{FLBEIA} function is a list containing information on the expected evolution of the fish stocks (\texttt{biols}), the fleets 
  (\texttt{fleets}), the covariates (\texttt{covars}), the provided advice (\texttt{advice}), the assessed stocks and observed indices 
  (\texttt{stocks} and \texttt{indices}), the control elements for the fleets (\texttt{fleets.ctrl}) and the versions of the different packages
  used to run the simulations (\texttt{pkgs.versions}). All the elements except \texttt{stocks} and \texttt{pkgs.versions} correspond with the
  updated versions of the objects used in the call to FLBEIA. 
  
  \noindent It has the following structure:
  \begin{center}
    \texttt{list(biols='FLBiols', fleets='FLFleetsExt', covars='FLQuants', advice='list(TAC,TAE,quota.share)', 
            stocks='FLStocks', indices='FLIndices', fleets.ctrl='list', pkg.versions='matrix') }
  \end{center}
  
  \noindent Description of the outputs:
    \begin{description}
      \item[\texttt{biols}:] \texttt{FLBiols} object containing historical and future "real" evolution of the stock.     
      \item[\texttt{fleets}:] \texttt{FLFleetsExt} object containing historical and future "real" evolution of the fleets 
  regarding effort exerted, distribution among metiers, catches, prices and so on.
      \item[\texttt{covars}:] Named list containing historical and future evolution of the different covariates.     
      \item[\texttt{advice}:] List containing information on management advice (e.g. TAC,TAE,quota.share).     
      \item[\texttt{stocks}:] Named list with one element per stock of class \texttt{FLStock} or \texttt{NULL}, if a \texttt{FLStock} is not needed to run the assessment.
          Contains the perceived stocks used in the management procedure to produce the management advice.
          For details on \texttt{FLStock} object see Figure~\ref{fig:FLStock}.
      \item[\texttt{indices}:] Named list with one element per stock of class \texttt{FLIndices} or \texttt{NULL}, if a \texttt{FLIndices} is not needed to run the assessment. 
      \item[\texttt{fleets.ctrl}:] Control object used for the \texttt{fleets.om} function.
      \item[\texttt{pkgs.versions}:] Matrix indicating the packages and package version used along the simulation.
    \end{description}
